Verifying Demonstrations

### 2017-10-06 protocol.tex
Adapts disposition of protocol sect, adapts to slides

\section{Protocol}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig) \\
      P\to S\colon & (pid, wid, t_s, l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

@@

\subsection{Verifying the proofs}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

  \pause{}

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}
}

\subsubsection{Participation-proof privacy}

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.
This is fine, since we do not want to catch any cheater, we just do not want to
count them more than once.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \pause{}

  \begin{idea}[Proof privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.

        \pause{}

      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
  \begin{remark}
    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
    signatures are linked with high probability.
  \end{remark}

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}

  \pause{}

  \begin{question}
    How to submit the proofs to the system?
  \end{question}
\end{frame}

\subsubsection{Receipt freeness}

@@

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item The proof itself is a sort of receipt.

        \pause{}

      \item If Eve compromises Alice's device, she can use it to verify that 
        she participated.

        \pause{}

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.
    \end{itemize}
  \end{remark}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.

        \pause{}

      \item E.g.\ a short-term and a long-term credential, then Alice can 
        drop the short-term credential.

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
}

  \pause{}

  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}

@@

\subsubsection{Architecture}

We also have an architectural problem.
If the system is only run by volunteering activists, then Eve can simply 
analyse network traffic and look for people running nodes in the system.

\begin{question}
  Shall we offer a platform that is run by a variety of institutions who 
  offers to verify protests?
  Or go strictly peer-to-peer?
\end{question}

\begin{question}
  If strictly peer-to-peer, and only run by protesters, one can infer that 
  they are protesters by running such a node.
  Can this be mitigated?
\end{question}

Similarly, we have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.
Otherwise Eve can analyse the network traffic to find out who submitted proofs 
to the system.
The main problem here is that the participants must be indistinguishable from 
non-participants.
This means that we cannot use special-purpose anonymizing 
technologies.

\begin{question}
  How do we submit the proofs to storage?
  Voting normally uses mix-nets (provable shuffles).
\end{question}

\begin{remark}
  We must mix participants with non-participants.
\end{remark}

>>>>

\mode*
\section{Protocol}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig) \\
      P\to S\colon & (pid, wid, t_s, l, wsig)
    \end{align*}
  \end{minipage}
  \mode<article>{%
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }}%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

@@

\subsection{Verifying the participation count}

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, i.e.\ of all its shares.

\subsubsection{Verifying eligibility}

To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
and \(wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.

@@

\subsubsection{Universal verifiability}

\dots

\subsubsection{Individual verifiability and receipt freeness}

\dots

@@

@@
